---
title: "Yext DataHub"
author: ""
date: "Last updated on `r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: "none"
    toc: true
    toc_depth: 3
    toc_float: true

---


<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
background-color: #00d188;
border-color: #00d188;
}

body {
font-family: FiraSans-Regular;
color: #444444;
font-size: 14px;
}

h1 {
font-weight: bold;
font-size: 28px;
}

h1.title {
font-size: 30px;
color: #00d188;
}

h2 {
font-size: 24px;
}

h3 {
font-size: 18px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.showtext = TRUE, 
                      dev = "svg"
                      # dpi = 700
)

knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})

# Sys.setlocale("LC_TIME", "C")
# extrafont::loadfonts(device = "win")
```



```{r prep}
## packages: remove or add your necessary packages

# required_packages <- c("tidyverse", "readxl", "ggthemes", "hrbrthemes", "extrafont", "plotly", "scales", "stringr", "gganimate", "here", "tidytext", "sentimentr", "scales", "DT", "here", "sm", "mblm", "glue", "fs", "knitr", "rmdformats", "janitor", "urltools", "colorspace", "pdftools", "showtext")
required_packages <- c("tidyverse")

for(i in required_packages) { 
  if(!require(i, character.only = T)) {
    
    #  if package is not existing, install then load the package
    install.packages(i, dependencies = T)
    require(i, character.only = T)
  }
}


## save plots?
save <- TRUE
#save <- FALSE

## quality of png's
dpi <- 750

## font adjust; please adjust to client´s website
#extrafont::loadfonts(device = "win", quiet = TRUE)
#font_add_google("Montserrat", "Montserrat")
# font_add_google("Overpass", "Overpass")
# font_add_google("Overpass Mono", "Overpass Mono")



## theme updates; please adjust to client´s website
#theme_set(ggthemes::theme_clean(base_size = 15))
theme_set(ggthemes::theme_clean(base_size = 15, base_family = "FiraSans-Regular"))


theme_update(plot.margin = margin(30, 30, 30, 30),
             plot.background = element_rect(color = "white",
                                            fill = "white"),
             plot.title = element_text(size = 20,
                                       face = "bold",
                                       lineheight = 1.05,
                                       hjust = .5,
                                       margin = margin(10, 0, 25, 0)),
             plot.title.position = "plot",
             plot.caption = element_text(color = "grey40",
                                         size = 9,
                                         margin = margin(20, 0, -20, 0)),
             plot.caption.position = "plot",
             axis.line.x = element_line(color = "black",
                                        size = .8),
             axis.line.y = element_line(color = "black",
                                        size = .8),
             axis.title.x = element_text(size = 12,
                                         face = "bold",
                                         margin = margin(t = 20)),
             axis.title.y = element_text(size = 12,
                                         face = "bold",
                                         margin = margin(r = 20)),
             axis.text = element_text(size = 11,
                                      color = "black",
                                      face = "bold"),
             axis.text.x = element_text(margin = margin(t = 10)),
             axis.text.y = element_text(margin = margin(r = 10)),
             axis.ticks = element_blank(),
             panel.grid.major.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.major.y = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.y = element_blank(),
             panel.spacing.x = unit(4, "lines"),
             panel.spacing.y = unit(2, "lines"),
             legend.position = "top",
             legend.title = element_text(family = "FiraSans-Regular",
                                         color = "black",
                                         size = 14,
                                         margin = margin(5, 0, 5, 0)),
             legend.text = element_text(family = "FiraSans-Regular",
                                        color = "black",
                                        size = 11,
                                        margin = margin(4.5, 4.5, 4.5, 4.5)),
             legend.background = element_rect(fill = NA,
                                              color = NA),
             legend.key = element_rect(color = NA, fill = NA),
             #legend.key.width = unit(5, "lines"),
             #legend.spacing.x = unit(.05, "pt"),
             #legend.spacing.y = unit(.55, "pt"),
             #legend.margin = margin(0, 0, 10, 0),
             strip.text = element_text(face = "bold",
                                       margin = margin(b = 10)))

## theme settings for flipped plots
theme_flip <-
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_line(size = .6,
                                          color = "#eaeaea"))

## theme settings for maps
theme_map <- 
  theme_void(base_family = "FiraSans-Regular") +
  theme(legend.direction = "horizontal",
        legend.box = "horizontal",
        legend.margin = margin(10, 10, 10, 10),
        legend.title = element_text(size = 17, 
                                    face = "bold"),
        legend.text = element_text(color = "grey33",
                                   size = 12),
        plot.margin = margin(15, 5, 15, 5),
        plot.title = element_text(face = "bold",
                                  size = 20,
                                  hjust = .5,
                                  margin = margin(30, 0, 10, 0)),
        plot.subtitle = element_text(face = "bold",
                                     color = "grey33",
                                     size = 17,
                                     hjust = .5,
                                     margin = margin(10, 0, -30, 0)),
        plot.caption = element_text(size = 14,
                                    color = "grey33",
                                    hjust = .97,
                                    margin = margin(-30, 0, 0, 0)))

## numeric format for labels
num_format <- scales::format_format(big.mark = ",", small.mark = ",", scientific = F)

# ## main color backlinko
# bl_col <- "#00d188"
# bl_dark <- darken(bl_col, .3, space = "HLS")
# 
# ## colors + labels for interval stripes
# int_cols <- c("#bce2d5", "#79d8b6", bl_col, "#009f66", "#006c45", "#003925")
# int_perc <- c("100%", "95%", "75%", "50%", "25%", "5%")
# 
# ## colors for degrees (Bachelors, Massters, Doctorate in reverse order)
# cols_degree <- c("#e64500", "#FFCC00", darken(bl_col, .1))
# 
# ## gradient colors for position
# colfunc <- colorRampPalette(c(bl_col, "#bce2d5"))
# pos_cols <- colfunc(10)
```


```{r}
# LOAD DATA
yext_data <- rio::import(here::here("proc_data", "yext_data.rds"))

```


# Background

The goal of the project is to showcase in a clear and elegant manner some findings from the [Yext DataHub](https://www.yext.com/search-data-hub) that are relevant for the clients of Rankings.io. This is useful and provides added value because the Yext DataHub is buggy, not easy to understand, and not focused on legal services. We requested a data extraction to Yext: all data about legal services in USA.

legal services


Data from : .  

Link to a "data dictionary": https://help.yext.com/hc/en-us/articles/360000001103-Available-metrics



# Data Preview

## Listings_Overview_Bar_YOY

This dataset corresponds to the left column of the "Metrics Overview" tab.

```{r, fig.align='center', fig.height=12, fig.width=16}

yext_data$Listings_Overview_Bar_YOY %>%
  ggplot(
    aes(x = date, y = `Measure Values`)
  ) +
  geom_col() +
  facet_wrap(facets = vars(`Measure Names`), ncol = 4)

```

* large effect of COVID on Google driving directions and Maps views. 
* same for Direct Queries. Start of the business again? 
* recent inncrease of Extended Network Clicks. ?


It seems that we don't have the data from the right column of the "Metrics Overview" tab: Pages Metrics YoY...  

## Longtail Impressions and Clicks - Search Network Clicks by Type

This data is in the tab "Search Network Listings Clicks" with a title of "Search Network Clicks by Type".  

**% Difference in Avg. Longtail Impressions Per Loc - YoY:**

```{r, fig.align='center', fig.height=4, fig.width=6}

yext_data$Longtail_Imps_YOY %>% 
  ggplot(
    aes(x = date, y = `% Difference in Avg. Longtail Impressions Per Loc`)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::percent)

```

**Longtail Impressions Per Loc - by month:**  

```{r, fig.align='center', fig.height=4, fig.width=6}

# useless because the scales are so different! 
# yext_data$Longtail_Imps_and_Clicks %>% 
#   pivot_longer(cols = c(`Avg. Longtail Clicks Per Loc`, `Avg. Longtail Impressions Per Loc`),
#                names_to = "Metric",
#                values_to = "Value") %>%
#   ggplot(aes(x = date, y = Value)) +
#            geom_line() +
#            facet_wrap(facets = vars(Metric), ncol = 1)

yext_data$Longtail_Imps_and_Clicks %>% 
  ggplot(aes(x = date, y = `Avg. Longtail Impressions Per Loc`)) +
  geom_line()

```


**% Difference in Avg. Longtail Clicks Per Loc - YoY:**  

```{r, fig.align='center', fig.height=4, fig.width=6}

yext_data$Longtail_Clicks_YOY %>% 
  ggplot(
    aes(x = date, y = `% Difference in Avg. Longtail Clicks Per Loc`)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::percent)

```

**Longtail Clicks Per Loc - by month:**    

```{r, fig.align='center', fig.height=4, fig.width=6}

yext_data$Longtail_Imps_and_Clicks %>% 
  ggplot(aes(x = date, y = `Avg. Longtail Clicks Per Loc` )) +
  geom_line()

```


## Google My Business Clicks by Type

These are the data from the tab "Google Listings Clicks".   

They are separated in several tables:  

* G_DDs_YOY
* G_DDs
* G_PCs_YOY
* ...

**Google Phone Calls Per Loc:**  
```{r, fig.align='center', fig.height=4, fig.width=6}

# only 2020 and 2021
yext_data$G_DDs_YOY %>%
  ggplot(aes(x = date, y = `Avg. Google Phone Calls Per Loc` )) +
  geom_line()

```

```{r, fig.align='center', fig.height=4, fig.width=6}

yext_data$G_PCs_YOY %>% 
  ggplot(aes(x = date, y = `% Difference in Avg. Google Phone Calls Per Loc` )) +
  geom_col() +
  scale_y_continuous(labels = scales::percent)
```

```{r, fig.align='center', fig.height=4, fig.width=6}

# all 3 years, we should prefer this one as the first above
yext_data$G_PCs %>%
  ggplot(aes(x = date, y = `Avg. Google Phone Calls Per Loc` )) +
  geom_line()

```

**Google Website Clicks Per Loc:**  
```{r, fig.align='center', fig.height=4, fig.width=6}

# only 2020-2021
yext_data$G_DDs_YOY %>%
  ggplot(aes(x = date, y = `Avg. Google Website Clicks Per Loc` )) +
  geom_line()

```

```{r, fig.align='center', fig.height=4, fig.width=6}

# exactly the same data as above, only 2020-2021
yext_data$G_PCs_YOY %>%
  ggplot(aes(x = date, y = `Avg. Google Website Clicks Per Loc` )) +
  geom_line()

```

```{r, fig.align='center', fig.height=4, fig.width=6}

# all 3 years, we should prefer this one as the two above
yext_data$G_PCs %>%
  ggplot(aes(x = date, y = `Avg. Google Website Clicks Per Loc` )) +
  geom_line()

```

```{r, fig.align='center', fig.height=4, fig.width=6}

yext_data$G_WCs_YOY %>%
  ggplot(aes(x = date, y = `% Difference in Avg. Google Website Clicks Per Loc` )) +
  geom_col() +
  scale_y_continuous(labels = scales::percent)
```

**Google Driving Directions Per Loc:**  
```{r, fig.align='center', fig.height=4, fig.width=6}

yext_data$G_DDs_YOY %>%
  ggplot(aes(x = date, y = `% Difference in Avg. Google Driving Directions Per Loc` )) +
  geom_col() +
  scale_y_continuous(labels = scales::percent)

```

```{r, fig.align='center', fig.height=4, fig.width=6}

yext_data$G_DDs %>%
  ggplot(aes(x = date, y = `Avg. Google Driving Directions Per Loc` )) +
  geom_line()

```

```{r, fig.align='center', fig.height=4, fig.width=6}

# THIS IS ONLY 2020 -> prefer G_DDs !
yext_data$G_PCs_YOY %>%
  ggplot(aes(x = date, y = `Avg. Google Driving Directions Per Loc` )) +
  geom_line()

```


## Google my Business Impressions - Google Listings Impressions

Data from the tab "Google Listings Impressions". 

Datasets: G_MVs_YOY and G_MVs.  

[plots here]


## ... 















